### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
H4, 5, & 6 and exploratory analyses

@@

@@

$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$

@@

@@

>>>>

```{r Hypothesis 4 Model}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

# running the models with revised QMP ratio's
H4_test_results_REV  <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)

@@

```{r Hypothesis 5 Model}
## Hypothesis 4 beta regression model
H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)

H5_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)

@@

$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$
```{r Hypothesis 6 Model}
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)

@@

```{r Hypotheses 5 & 6 Sensitivity Analyses}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
data_h5_sens$QMP_REV <- log(data_h5_sens$QMP_REV_ratio /(1 - data_h5_sens$QMP_REV_ratio))

check_h5 <- lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
H5_sensitivity_test_results <- summary(check_h5)$coefficients

check_h5_REV <- lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
H5_sensitivity_test_results_REV <- summary(check_h5_REV)$coefficients

## Hypothesis 6 sensitivity test using a random intercept Guassian model.
# create dummy H6 dataframe for use in sensitivity test
data_h6_sens <- data_h6

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))
data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))

# running the models one with none revised QMP ratio's and one with
check_h6 <- lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens)
H6_sensitivity_test_results <- summary(check_h6)$coefficients

check_h6_REV <- lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens)
H6_sensitivity_test_results_REV <- summary(check_h6_REV)$coefficients

# n of mod ratio's pressent check
H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n

```{r Hypothesis 6 Associations}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding)
Results_H6_between <- Associations_H6(data_h6)

# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
# of a concern for the revised.

# Associations between the QMP categories (revised QMP coding)
Results_H6_between_REV <- Associations_H6_REV(data_h6)

@@

```{r Unidimensionality Exploratory Analysis}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                            data_1.12.3.2_clean, data_2.10.1_clean,
                            data_2.12.1_clean, data_2.12.2_clean, 
                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
                            data_2.23_clean, data_3.2.1.1_clean, 
                            data_3.2.1.2_clean, data_3.7.1_clean, 
                            data_3.7.2_clean, data_3.8.2_clean,
                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)

# creating an empty dataframe to store the results in
cfa_results <- data.frame(RMSEA = 0,
                          N_factors = 0,
                          Single_factor = FALSE)

# running the cfas for all of the extracted datasets
for (i in 1:length(extracted_data_list)){
  # obtaining single factor model cfa RMSEA value for evaluation
  RMSEA_value <- fa(extracted_data_list[[i]][-1])$RMSEA[1]

  # conducting parallel test to check if one factor solution is best.
  parallel_N_factors <- fa.parallel(extracted_data_list[[i]][-1], 
                                    fa = "fa")$nfact

  # adding a single factor check indicator value
  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, TRUE, 
                          FALSE)

  # adding the cfa results of one factor analysis to the results dataframe.
  cfa_results <- rbind(cfa_results, c(RMSEA_value, parallel_N_factors, 
                                      single_factor))
}
# removing the initial empty row
cfa_results <- cfa_results[-1,]
